Boundary Labeling for annotated documents

### 2017-11-05 LaTeX/Paper.tex
Paper: Modified Section 2. Program: Changes from previous commit (new Debug variable) failed to commit. Adding them now.

In our labeling algorithm, we decided to work through the labels in the order they appear in the text, placing each as far up as possible, and skipping any label that would've required us place the label below its leader's source node. We also opted to use fixed ports located in the top left corner of each label, as this allowed us to unabiguously place annotations by only knowing their port location, which is equal to their leader's ending point. To not restrict the label's placement by the line spacing, we left a buffer zone between the text area and the label area, which allows us to place labels even further above to optimally use the available space.
The routing was implemented using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex, prioritizimg locations above whenever possible. After the algorithm terminates, it returns a path from the site to the right text border and information on where to draw the OPO-segment that connects the text area with the label's port, if successful.

>>>>

In our labeling algorithm, we decided to work through the labels in the order they appear in the text, placing each as far up as possible, and skipping any label that would've required us place the label below its leader's source node. We also opted to use fixed ports located in the top left corner of each label, as this allowed us to unabiguously place annotations by only knowing their port location, which is equal to their leader's ending point. To not restrict the label's placement by the line spacing, we left a buffer zone between the text area and the label area, which allows us to place labels even further above to optimally use the available space.
The algorithm's input consists of the Graph $G$ and a set of sites $V_{ann} \subset V$ which will be routed using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex, prioritizing moving up whenever possible. After the algorithm terminates, it returns a set with routing information for each vertex, which contains a Path $P=\{v_1, \cdots, v_n\}$, leading from the site to the text area's border, along with some additional information on how to draw the OPO-Segment that connects to the Label's port. If the routing for any given site failed, the path consists of a single vertex - the site.
